Research training portfolio

### 2012-11-08 Research training portfolio.tex
RTP: added abstract and more evaluation

@@

@@

@@

In this section, I describe the various evaluation measures I used. This is necessary because evaluation of spelling corrector has not been very uniform in the spelling checker literature so far; whereas various scholars only measured how many errors their algorithm can detect in an error list and called it accuracy (e.g. Agirre et al., 1998; Brill \& Moore, 2000; Toutanova \& Moore, 2002; \citet{tm02,vandelden04}), others use or argue for the precision-recall terminology (Reynaert, 2008; Pollock \& Zamora, 1984, although they use other terms for the two concepts) or argue against it \citep{sp02}.\\\indent

Although most of the evaluation measures used can be useful and informative, they only tell part of the story. I think it is important to recognize that spelling correction is a multi-step process, and each step comes with its own measures. Using a confusible corrector as part of a spelling corrector, there are three steps: word prediction, error detection and error correction. I'll go through these steps and their evaluation measures one by one.

@@

\begin{itemize}
\item Prediction accuracy. Although word prediction may be the most complicated part of the confusible corrector, its evaluation is actually the simplest. Calculating prediction accuracy entails removing all confusibles from a text, and see in how many of the cases the language model can correctly predict which word was removed. This percentage can be increased by only counting predictions that are above a certain threshold. Results with multiple thresholds (i.e. to what extent does the prediction accuracy improve if the threshold is raised) can be visualized with a graph, as shown in the result section.
\end{itemize}

@@

\begin{itemize}
\item The confusion matrix. From this step onwards, we concentrate on spelling errors. This means that our input no longer is errorless text (like in the previous step). We also interpret the results of the prediction differently now: whereas incorrectly predicted words were considered errors of the system in the previous task, lowering the accuracy, they will now be considered corrections. This means that the system can do two things right (correct incorrect words in the text and don't correct correct words), and two things wrong (correct correct words and don't correct incorrect words). This can be summarized in a confusion matrix (taken from \citet{fawcett04}):

@@

@@

It is similar to prediction accuracy in that it indicates how well the sytem does in general, but keep in mind that they're measuring two completely different concepts. Although a system with a good prediction accuracy also has a good detection accuracy, it might be possible that a system very good at predicting confusibles in errorless texts behaves differently in texts that do contain errors.

@@

\paragraph{Error correction} Some text.

>>>>

\let\stdsection\section
\renewcommand\section{\newpage\stdsection}

@@

\subsection*{Abstract}

For many confusibles, like '/emph{you're} versus /emph{your}', one option is much more frequent than the other. This poses a problem when one tries to create a context-sensitive memory-based confusible corrector, as having more data for one option will make it more likely that the confusible corrector will predict that option. In some cases this can be solved by balancing the training data so that it has exactly the same amount of examles for each option, but in other cases this means a very large part of the data have to be thrown away, making the corrector even worse. In this paper I investigate %ja, wat eigenlijk?

@@

Dit is een confusible. Zo kan je ze herkennen. Dit hebben andere mensen gedaan. Dit zijn de confusibles waarnaar ik ga kijken. Dit zijn de verdelingen in mijn testset... kijk ze zijn scheef. Ik kan ze niet altijd weggooien, want dat wordt het nog erger.

@@

In this section, I describe the various evaluation measures I used. This is necessary because evaluation of spelling correctors has not been very uniform in the spelling checker literature so far; whereas various scholars only measured how many errors their algorithm can detect in an error list and called it accuracy (e.g. \citealp{agirre98, bm00, tm02,vandelden04}), others use or argue for the precision-recall terminology (\citealp{reynaert08,pz84}, although they use other terms for the two concepts) or argue against it \citep{sp02}.\\\indent

Although most of the evaluation measures used in the literature can be useful and informative, they only tell part of the story. I think it is important to recognize that spelling correction is a multi-step process, and each step comes with its own measures. When using a confusible module as part of a spelling corrector, there are three steps: word prediction, error detection and error correction. I'll go through these steps and their evaluation measures one by one.

@@

\begin{itemize}
\item Prediction accuracy. Although word prediction may be the most complicated part of the confusible module, its evaluation is actually the simplest. Calculating prediction accuracy entails removing all confusibles from a text, and see in how many of the cases the language model can correctly predict which word was removed. This percentage can be increased by only counting predictions that are above a certain threshold. Results with multiple thresholds (i.e. to what extent does the prediction accuracy improve if the threshold is raised?) can be visualized with a graph, as shown in the result section.
\end{itemize}

@@

\begin{itemize}
\item The confusion matrix. From this step onwards, we concentrate on spelling errors. This means that our input no longer is errorless text, like in the previous step. We also interpret the results of the prediction differently now: whereas incorrectly predicted words were considered errors of the system in the previous task, lowering the accuracy, they will now be considered corrections. This means that the system can do two things right (correct incorrect words in the text and don't correct correct words), and two things wrong (correct correct words and don't correct incorrect words). This can be summarized in a confusion matrix (taken from \citet{fawcett04}):

@@

When reporting the results of a confusible module, the names of the various cells will be replaced by numbers. These numbers are the data needed to calculate various evaluation measures, like the three below. Beside these evaluation measures, I will always give the confusion matrix itself, so readers can calculate other measures if desired.

@@

It is similar to prediction accuracy in that it indicates how well the sytem does in general, but keep in mind that prediction and detection accuracy measure two completely different concepts. Although a system with a good prediction accuracy is very likely to also have a good detection accuracy, it might be possible that a system very good at predicting confusibles in errorless texts behaves differently in texts that do contain errors.

@@

\paragraph{Error correction}

\begin{itemize}
\item Confusion matrix.
\item Detection accuracy.
\item Detection recall.
\item Detection precision.
\end{itemize}
